Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-06 paper/ms.tex
minor edits in discussion

However, the same Figure \ref{fig:mmed} shows something interesting
that semi-analytical approaches were not able to predict.
The mass width, $\Delta M{1\sigma}$, that is the width of the mass
distribution for a given model with fixed $\mmin$ and $\mmax$, has a
median value and $1\sigma$ uncertainty of $\Delta M{1\sigma} =
0.55^{+0.11}_{-0.31}$ dex.
This means that the mass range for halos hosting LAEs is very narrow,
there is only a factor of $2$ to $4$ between the lower and upper mass
boundary.

In summary, the median mass could be anything in the range
$10^{9.5}$\hMsun and $10^{11.5}$, but the width is highly constrained
to be between $0.2$ and $0.6$ dex.

>>>>

However, the same Figure \ref{fig:mmed} shows something 
that semi-analytical approaches were not able to predict.
The mass width, $\Delta M_{1\sigma}$, that is the width of the mass
distribution for a given model with fixed $\mmin$ and $\mmax$, has a
median value and $1\sigma$ uncertainty of $\Delta M_{1\sigma} =
0.55^{+0.11}_{-0.31}$ dex.
This means that the mass range for halos hosting LAEs is very narrow.
There is only a factor of $2$ to $4$ between the lower and upper mass
boundary.

Summarizing, the median mass could be anything in the range
$10^{9.5}$\hMsun and $10^{11.5}$ (a $2.0$ dex range), but the width is
highly constrained to be between $0.2$ and $0.6$ dex.
